Market simulator

### 2020-10-30 analysis/05_market_simulator.Rmd
Added req() helps with initial loading of data

# Organization configuration
organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_data <- read_csv(
      here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
    )
  } else {
    organization_data <- read_csv(input$org_update$datapath)
  }
})

# Persona configuration
persona_data <- reactive({
  if (is.null(input$per_update$datapath)) {
    persona_data <- read_csv(
      here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
    )
  } else {
    persona_data <- read_csv(input$per_update$datapath)
  }
})
```

@@

# Render the organization configurations as a table
renderTable({
  org_import = read_csv(input$org_update$datapath)

  org_import
})

# Render the persona configurations as a table
renderTable({
  per_import = read_csv(input$per_update$datapath)

  per_import
})
```

>>>>

# Organization configuration
organization_data <- reactive({
  if (is.null(input$org_update$datapath)) {
    organization_data <- read_csv(
      here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
    )
  } else {
    req(input$org_update)
    organization_data <- read_csv(input$org_update$datapath)
  }
})

# Persona configuration
persona_data <- reactive({
  if (is.null(input$per_update$datapath)) {
    persona_data <- read_csv(
      here::here('analysis', 'output', 'configurations', 'persona_config01.csv')
    )
  } else {
    req(input$per_update)
    persona_data <- read_csv(input$per_update$datapath)
  }
})
```

@@

# Render the organization configurations as a table
renderTable({
  req(input$org_update)

  org_import = read_csv(input$org_update$datapath)
  org_import
})

# Render the persona configurations as a table
renderTable({
  req(input$per_update)

  per_import = read_csv(input$per_update$datapath)
  per_import
})
```
